A thesis draft

### 2018-11-09 res/sections/08-Background.tex
Polpetta's review

\subsection{The SDN stack}
\begin{figure}[t]
 \centering
 \includegraphics[scale=1.3]{sdn_architecture}
 \caption{SDN architecture}
 \label{chap:background:img:sdn_architecture}
\end{figure}
As depicted in Figure~\ref{chap:background:img:sdn_architecture} the SDN
architecture can be splitted in three different layers, based on their
functionalities. \emph{SDN Applications} are programs that communicate the
behaviour to the SDN controllers and request for needed resources and data
through APIs, often called \emph{northbound interfaces}(NBI). NBIs add a level
of abstraction to the higher level application on the set of functionalities of
the controllers: ideally, taking advantage of NBIs, application could use
controllers of different vendors in the same way. So, SDN applications can be
seen as 2 layers programs, the logic and the communication part that uses NBIs.
Theese applications can also build an abstracted view of the network, using
information of controllers, in order to make easier the analysis of the traffic
and simplifing the decision making process.

@@

The analysis of this topic revealed to be trivial: since internet has many
different protocols that would become infeasible to support all of them at the
same time, packet incapsulation present itself as the only faseable solution:
every packet incoming in the VNFs has already been encapsulated by a generic
packet incapsulator/decapsulator,
\todo{Also I think that the main purpose of UDP encapsulation is not to hide 
the protocol used on the edges but 1) usa a ``quick protocol to exchange data 
among VNFs and 2) we are hiding the path not the protocol itself. As we were 
discussing, we are creating some sort of proxy, so the aim will be the same 
even if we support a plethora of protocols.''} making the whole architecture 
indipendent from the protocol a particolar flux of data. To achieve this, 
several solutions have been studied, and at the end packet incapsulation with 
TCP split (for TCP sessions) have been choosen. The rationale that guided us on 
this choice is described in Chapter~\ref{chap:vnf_ns_impl}. \todo{Update 
reference with the section of the explanation}

>>>>

\subsection{The SDN stack}
\begin{figure}[t]
 \centering
 \includegraphics[scale=1.3]{sdn_architecture}
 \caption{SDN architecture}
 \label{chap:background:img:sdn_architecture}
\end{figure}
As depicted in Figure~\ref{chap:background:img:sdn_architecture} the SDN
architecture can be splitted in three different layers, based on their
functionalities. The \emph{SDN Applications} role is to set the 
behaviour of the SDN controllers and manage its hardware resources and data 
through APIs, often called \emph{northbound interfaces}(NBI).
These interfaces provide an additional abstraction layer that high-level 
applications can consume, enabling the possibility to use a variety of 
different verdors' controllers in the same way.
Analysing the SDN applications is possible to note two defined layers, one that 
is responsible to manage the whole logic, and another one dedicated to the 
communication part, that in particular uses the previsously defined NBIs.
Theese applications can also build an abstracted view of the network, using
controllers information, in order to make the traffic analysis easier and to 
simplify the decision making process.

@@

The analysis of this topic revealed to be trivial: since internet has many
different protocols that would become infeasible to support all of them at the
same time, packet incapsulation present itself as the only faseable solution:
every packet incoming in the VNFs has already been encapsulated by a generic
packet incapsulator/decapsulator,
\todo{Also I think that the main purpose of UDP encapsulation is not to hide 
the protocol used on the edges but 1) usa a ``quick protocol to exchange data 
among VNFs and 2) we are hiding the path not the protocol itself. As we were 
discussing, we are creating some sort of proxy, so the aim will be the same 
even if we support a plethora of protocols.''} making the whole architecture 
indipendent from the protocol a particular flux of data. To achieve this, 
several solutions have been studied, and at the end packet incapsulation with 
TCP split (for TCP sessions) have been choosen. The rationale that guided us on 
this choice is described in Chapter~\ref{chap:vnf_ns_impl}. \todo{Update 
reference with the section of the explanation}
